Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
Added plots for 6 and 50 body simulations.
NM

The vorticity field not only allows us to visualize regions of high shear, but also allows us to identify preferred channels with most intense flow. Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6. This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6) follow. Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode. This can be seen by the overall vorticity magnitude growing in time. By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/06plots.pdf}
\caption{\label{fig:06plots} plots to go with 6 body simulation.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

>>>>

The vorticity field not only allows us to visualize regions of high shear, but also allows us to identify preferred channels with most intense flow. Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6. This main channel widens the fastest, and secondary channels follow (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6). Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode. This can be seen by the overall vorticity magnitude growing in time. By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.95 \textwidth]{./figs/mbodyplots.pdf}
\caption{\label{fig:mbodyplots} plots to go with 6 body simulation.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
